Response to the defense feedback

### 2021-06-03 Chapter-5/Chapter-5.tex
Updates from Overleaf

Second, many side-channel leakage detection tools rely on
techniques such as symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Due
to the limitations of existing binary analysis techniques, it is hard to apply existing methods to analyze side-channels in non-cryptography
libraries. For many other applications like machine learning, media,
and graphic libraries built on the top architecture-dependent
libraries (e.g., Intel MKL~\cite{wang2014intel}), these tools are not able to
handle them. Moreover, some binary analysis frameworks (e.g.,
Angr~\cite{shoshitaishvili2016state}) are limited in analyzing
floating-point instructions. However, the functionality of those
applications heavily depends on floating-point calculations.

Third, while many existing works can detect side-channel leakages, few
of them can assess the severity levels of those
vulnerabilities~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus,236334,wang2021data,sung2018canal}.
Some existing tools~\cite{182946,chattopadhyay2019quantifying, biondi2018scalable,5207642,pasareanu2016multi,AskarovC12,phan2017synthesis} quantify the information leakage by giving an upper
bound estimation of each leakage site.  This is helpful to justify that the software is secure if the reported leakage is zero. However,
those tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.  Often the over-approximated estimate is very far away from the amount of real leakage.
For example, CacheAudit~\cite{182946} estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even those
tools report severe leakage, it does not mean the program has a truly severe leakage.

>>>>

Second, many side-channel leakage detection tools rely on
techniques such as symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Due
to the limitations of existing binary analysis techniques, it is hard to apply existing methods to analyze side-channels in non-cryptography
libraries. For many other applications like machine learning, media,
and graphic libraries built on the top architecture-dependent
libraries (e.g., Intel MKL~\cite{wang2014intel}), these tools are not able to
handle them. Moreover, some binary analysis frameworks (e.g.,
Angr~\cite{shoshitaishvili2016state}) are limited in analyzing
floating-point instructions. However, the functionality of these
applications heavily depends on floating-point calculations.

Third, while many existing works can detect side-channel leakages, few
of them can assess the severity levels of these
vulnerabilities~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus,236334,wang2021data,sung2018canal}.
Some existing tools~\cite{182946,chattopadhyay2019quantifying, biondi2018scalable,5207642,pasareanu2016multi,AskarovC12,phan2017synthesis} quantify the information leakage by giving an upper
bound estimation of each leakage site.  This is helpful to justify that the software is secure if the reported leakage is zero. However,
these tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.  Often the over-approximated estimate is very far away from the amount of real leakage.
For example, CacheAudit~\cite{182946} estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even those
tools report severe leakage, it does not mean the program has a truly severe leakage.
